\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Rakesh}{Sukla}{ % Your name
\urlstyle{same}\url{https://github.com/rakeshsukla53} \\ % Your website, Linked-In profile or other web address
\href{mailto:rrs402@nyu.edu}{rrs402@nyu.edu} | 302-438-5450 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{New York University}

\descript{MS in Computer Science}
\location{Expected Dec 2015 | New York \\ GPA: 3.6}

\sectionspace % Some whitespace after the section
\subsection[Bharati Vidyapeeth's  college of Engineering]{\texorpdfstring{Bharati Vidyapeeth's\\ college of Engineering}{}}
\descript{BS in Electronics and Communication}
\location{2008-2012 | New Delhi, India }
\location{GPA: 3.6/ 4.0}

%------------------------------------------------
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/rakeshsukla53}{\bf rakeshsukla53} \\
LinkedIn:// \href{https://www.linkedin.com/in/rakeshsukla}{\bf rakeshsukla}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Design and Analysis of Algorithm \\
Software Defined Networking \\
Cloud Computing \\ 
Computer Architecture

\sectionspace % Some whitespace after the section

%------------------------------------------------

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}
Python \textbullet{} R \textbullet{} Shell \textbullet{} JavaScript \textbullet{} C++
\subsection{Database}
PostgreSQL \textbullet{} MS SQL Server \\ \textbullet{} DynamoDB \textbullet{} MongoDB
\subsection{Data Analysis}
OpenRefine \textbullet{} Tableau \textbullet{} Drake \textbullet{} Apache Hive \textbullet{} Apache Spark
\textbullet{} Map-Reduce
\subsection{AWS}
EC2 \textbullet{} S3 \textbullet{} EMR \textbullet{} API Gateway \\ \textbullet{} DynamoDB
\subsection{Reporting Tools}
Oracle BI Publisher \textbullet{} SQR \textbullet{} PS Query 
\subsection{Framework}
Django \textbullet{} Tornado

\sectionspace % Some whitespace after the section
\section{Awards} 

\begin{tabular}{rll}
2014-2015& Graduate Merit \\ &Scholarship\\
2008-2012& Prime Minister's \\ 
&Scholarship for Bachelor's \\ &Degree 
\end{tabular}




%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Oak Hill Advisors, L.P.}
\descript{| Software Engineer Intern}
\location{June 2015 – August 2015 | New York}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Created a web application which extracts correct information with accuracy of more than 90 percent from the pdf files, the final output is an excel file.
\item Developed email scrubber which filters and downloads attachments from Microsoft Outlook. The tool is used everyday by team now.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Ontodia}
\descript{| Data Analyst Intern}

\location{Feb 2015 – May 2015 | New York}
\begin{tightitemize}
\item Cleaned datasets using open-refine, R and wrote automation scripts in Python.
\item Created Carto-DB report to visualize the data.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Accenture}
\descript{| Software Engineer}

\location{Feb 2013 – July 2013 | Mumbai, India}
\begin{tightitemize}
\item Developed Financial Intergrated Systems for the State of California using Peoplesoft Technology. This application will be used by more than 1 million people by 2018. 
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------

\section{TECHNICAL PROJECTS}

\runsubsection{Collaborator}
\location{Mar 2015- May 2015 | New York}
Built a web application through which you can match your profile with other students and build connection. If your personality and skills have greater than 70 percent match then you can directly call, message and send request on Facebook/Linkedln. Tool is used by students to find project partner.   
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Twitter Sentiment} 
\location{Mar 2015 – May 2015 | New York}
Developed an application through which you can use analyze tweet sentiment on Google heat map.
\sectionspace % Some whitespace after the section

\runsubsection{Open Street Map} 
\location{August 2015 | New York}
To overcome the problem of geocoding limits on Google Maps, Yahoo or Bing, we created our own server using openstreet data. We loaded the whole US data on the server so that now we can do unlimited geocoding.
\sectionspace % Some whitespace after the section

\runsubsection{SDN Firewall and Load Balancer} 
\location{Nov 2014 | New York}
Implemented a customized network, which consists of virtual hosts, switches, and controller on Mininet. Wrote Firewall functionality on openflow switches using POX controller. Executed Firewall and Mac learning module using pyretic policies on RYU Controller.
\sectionspace % Some whitespace after the section

\runsubsection{Netflix Analysis Map Reduce} 
\location{May 2014 | New York}
Performed analysis of Netflix Data using Map Reduce. Determined which is the most viewed movie, from where most number of hits are coming from. Analyzed the number of hits to the site made by each different IP Address.
\sectionspace % Some whitespace after the section

\runsubsection{RSS Feed downloader} 
\location{Dec 2015 | New York}
Developed a RSS feed crawler that will extract the files from the link and place it on server. Performed data cleaning, manipulation and testing with the index files downloaded from the website.
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------


\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}